\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[legalpaper, margin=.5in]{geometry}
\title{Testing Plan}
\author{Josh Carroll & James Driver}
\date{February 27th, 2023}
\begin{document}
\begin{titlepage}
   \begin{center}
       \vspace*{1cm}

       \textbf{Test Plan}

       \vspace{0.5cm}
        Zerg Mining Expedition
            
       \vspace{1.5cm}

       \textbf{Josh Carroll, James Viner \& Raymone Miller}

       \vfill
            
       \vspace{0.8cm}
            
       Tool Developer Qualification Course\\
       UMBC\\
       February 27th, 2023
            
   \end{center}
\end{titlepage}
\noindent\Huge\textbf{Test Plan, Mining}\\
\\
\Large{The program is designed to be an API which will help a developer in coding
an actual program. This API will consist of Zerg overlords and Zerg Drones.
The overlords will send drones out upon mining expeditions to collect and
bring back minerals that the Zerg race need to survive. As these drones are
deployed and explore the map they will suggest a route that is the best path
to the minerals according to the drone’s current knowledge of the map.}\\
\\

\\
\noindent\Large\textbf{Instructor provided Files}
\begin{itemize}
  \item \textbf{~/timeout.py}\\
  {Defines functions needed for a program timeout.}
   \item \textbf{~/map.py}\\
  {defines location, map, mineral context, and drone context classes.}
   \item \textbf{~/begin\_mining\_expedition.py}\\
  {attempts to run a mining expedition w/ data types needed.}
   \item \textbf{~/sample\_classes.py}\\
  {defines dashboard, Drone and Overlord classes.}
     \item \textbf{~/maps}\\
  {contains test maps.}
\end{itemize}

\noindent\Large\textbf{Sample Files}
\begin{itemize}
  \item \textbf{None yet listed}\\
\end{itemize}

\Large\textbf{TC1:Installation}
\begin{enumerate}
    \item \textit{git clone git@git.umbc.tc:tdqc/tdqc12/carroll/mining.git}
    \item \textit{cd mining}\\
    \textbf{Expected:}{mining directory is created}\\
\end{enumerate}
\large{prerequisites: In mining directory}\\
\Large\textbf{TC2:Correct Branch}
\begin{enumerate}
    \item \textit{git branch}\\
    \textbf{Expected:}{main is default branch}
\end{enumerate}

\noindent\huge\textbf{Common Test Cases}\\
\end{document}

